True versus apparent shapes of bow shocks

### 2017-12-03 papers/Paper1/sec-conclusions.tex
Describe the simulation planitude-alatude tracks

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
  \caption[]{Apparent projected shapes of simulations in the
    \(\Pi'\)--\(\Lambda'\) plane.  Thick solid lines show the predicted
    inclination-dependent tracks of the traced contact discontinuity
    shape, with tick marks indicating 20 equal intervals in
    \(\abs{\sin i}\). Open square symbols show the shapes traced from
    the dust emission maps at \SI{60}{\um} for inclinations of
    (largest to smallest) \ang{30}, \ang{45}, and \ang{60}. For
    comparison, the wilkinoid track is shown in white. Note that the
    scales of both axes are logarithmic in this case.}
  \label{fig:sim-Pi-Lambda}
\end{figure}

The resultant inclination-dependent tracks in the planitude--alatude plane are shown in

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
  \caption[]{Apparent projected shapes of simulations in the
    \(\Pi'\)--\(\Lambda'\) plane.  Thick solid lines show the predicted
    inclination-dependent tracks of the traced contact discontinuity
    shape, with tick marks indicating 20 equal intervals in
    \(\abs{\sin i}\). The true planitude and alatude are marked by
    filled circle symbols.  Open square symbols show the shapes traced
    from the dust emission maps at \SI{60}{\um} for inclinations of
    (largest to smallest) \ang{30}, \ang{45}, and \ang{60}. For
    comparison, the wilkinoid track is shown in white. Note that the
    scales of both axes are logarithmic in this case.}
  \label{fig:sim-Pi-Lambda}
\end{figure}

The resultant inclination-dependent tracks in the planitude--alatude
plane are shown in Figure~\ref{fig:sim-Pi-Lambda}.  These are compared
with measurements\footnote{%
  The shape measurements were performed by converting to contours the
  \SI{60}{\um} images in \citet{Meyer:2017a}'s Fig.~10 and then
  tracing around the bow the ridge of minimum radius of curvature of
  the contours.} %
from post-processed infrared dust continuum maps \citep[\S~4.3
of][]{Meyer:2017a}, shown by open square symbols for \(i = \ang{30}\),
\ang{45}, and \ang{60}.
